Enhancing Adversarial Robustness for Deep Metric Learning

### 2022-01-24 reb/RebuttalTemplate.tex

\documentclass[10pt,twocolumn,letterpaper]{article}
\usepackage[rebuttal]{cvpr}

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref,breaklinks,colorlinks,bookmarks=false]{hyperref}

% Support for easy cross-referencing
\usepackage[capitalize]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}

% If you wish to avoid re-using figure, table, and equation numbers from
% the main paper, please uncomment the following and change the numbers
% appropriately.
%\setcounter{figure}{2}
%\setcounter{table}{1}
%\setcounter{equation}{2}

% If you wish to avoid re-using reference numbers from the main paper,
% please uncomment the following and change the counter for `enumiv' to
% the number of references you have in the main paper (here, 6).
%\let\oldthebibliography=\thebibliography
%\let\oldendthebibliography=\endthebibliography
%\renewenvironment{thebibliography}[1]{%
%     \oldthebibliography{#1}%
%     \setcounter{enumiv}{6}%
%}{\oldendthebibliography}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{201}% *** Enter the CVPR Paper ID here
\def\confName{CVPR}
\def\confYear{2022}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Enhancing Adversarial Robustness for Deep Metric Learning -- Author Response}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}
\appendix

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section{To Reviewer \#1}

This manuscript investigates the joint area of DML and robustness against adversarial attacks of deep model. I understand that some DML applications may require robustness. However, the potential impact of the research topic is limited. From my view, the DML models are not special in terms of robustness against adversarial attacks compared to other deep models.

Another non-negligible problem is the discussion of the relationship between the proposed method and a series of adversarial training algorithms is missing. I’m hoping that the author could complete it in the related works section, including reference 29. “Sat: Improving adversarial training via curriculum-based loss smoothing” in the original manuscript and some other studies, such as [1] and [2]. I think the idea of the proposed method bears a certain similarity to these.

[1]. Cai, Qi-Zhi, et al. "Curriculum adversarial training." arXiv preprint arXiv:1805.04807 (2018).

[2]. Zhu, Xiaojin. "An optimal control view of adversarial machine learning." arXiv preprint arXiv:1811.04422 (2018).

\section{To Reviewer \#2}

- Paper is sometimes hard to read, sentences tend to be too long and complex, method abbreviations are confusing and hard to remember.

- Tables are hard to grasp at a first glance, too many abbreviations and notations. It would be useful to make captions self explanatory and refresh the notation in them so that I dont have to search for them in different places of the paper. Also, some color coding or marking the most important results would be useful it is hard to ONE table with 20 rows and 20 columns, even harder with 5 such tables.

- Paragraph on memory and time complexity between methods missing, are they all equal?

\section{To Reviewer \#3}

1. Robustness is important and many novel methods have been proposed, e.g., TRADES and AWP. I wonder whether these methods are not suitable for the metric learning task, and why the robustness of the metric learning task is unique.

2. The main motivation of this work is that previous works suffer from excessively hard examples and this work aims to control the hardness. Does simple tricks like mixup work for adjusting the hardness.

3. Tables (e.g., Tab.3) is hard to read. The authors may need to re-organize them and highlight somewhere.

4. The performance on benign examples seems to drop a lot. Does it mean the HM is just another trade-off way?

%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

\end{document}

### 2022-01-24 reb/RebuttalTemplate.tex

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Enhancing Adversarial Robustness for Deep Metric Learning -- Author Response}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}
\appendix

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section*{To Reviewer \#1}

\noindent\textbf{Q1.}
%
\ul{
From my view, the DML models are not special in terms of robustness against
adversarial attacks compared to other deep models.
}

\noindent\textbf{Q2.}
%
\ul{
The discussion of the relationship between the proposed method and a series of
adversarial training algorithms is missing.
}

I’m hoping that the author could complete it in the related works section,
including reference 29. “Sat: Improving adversarial training via
curriculum-based loss smoothing” in the original manuscript and some other
studies, such as [1] and [2]. I think the idea of the proposed method bears a
certain similarity to these.

@@

[1]. Cai, Qi-Zhi, et al. "Curriculum adversarial training." arXiv preprint arXiv:1805.04807 (2018).

[2]. Zhu, Xiaojin. "An optimal control view of adversarial machine learning." arXiv preprint arXiv:1811.04422 (2018).

\section*{To Reviewer \#2}

\noindent\textbf{Q1.}
%
\ul{
Sentences tend to be too long and complex; Method abbreviations are confusing
and hard to remember.
}

\noindent\textbf{Q2.}
%
\ul{
Tables are hard to grasp at a first glance, too many abbreviations and
notations. It would be useful to make captions self explanatory and refresh the
notation in them so that I dont have to search for them in different places of
the paper. Also, some color coding or marking the most important results would
be useful it is hard to ONE table with 20 rows and 20 columns, even harder with
5 such tables.
}

\noindent\textbf{Q3.}
%
\ul{
Paragraph on memory and time complexity between methods missing, are they all
equal?
}

@@

\section{To Reviewer \#3}

\noindent\textbf{Q1.}
%
\ul{
Robustness is important and many novel methods have been proposed, e.g., TRADES and AWP. I wonder whether these methods are not suitable for the metric learning task, and why the robustness of the metric learning task is unique.
}

\noindent\textbf{Q2.}
%
The main motivation of this work is that previous works suffer from excessively hard examples and this work aims to control the hardness. Does simple tricks like mixup work for adjusting the hardness.

\noindent\textbf{Q3.}
%
Tables (e.g., Tab.3) is hard to read. The authors may need to re-organize them and highlight somewhere.

\noindent\textbf{Q4.}
%
The performance on benign examples seems to drop a lot. Does it mean the HM is just another trade-off way?

### 2022-01-26 reb/RebuttalTemplate.tex

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Enhancing Adversarial Robustness for Deep Metric Learning -- Author Response}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}
\appendix

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section*{To Reviewer \#1}

\noindent\textbf{Q1.}
%
\ul{
The DML models are not special in terms of robustness against
adversarial attacks compared to other deep models.
}

\textbf{A:} 
%
We agree with the reviewer. Adversarial robustness at the visual representation
level remains to be an open but insightful problem. Since deep metric learning
can be interpreted as ``representation learning in metric space'', we believe
the defense for deep metric learning is one step closer to the
representation-level robustness, and may inspire future works for 
robustness disentangled from specific vision tasks.

### 2022-01-26 reb/RebuttalTemplate.tex

\documentclass[10pt,twocolumn,letterpaper]{article}
\usepackage[rebuttal]{cvpr}

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage{soul}
\usepackage{xpatch}

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref,breaklinks,colorlinks,bookmarks=false]{hyperref}

%%START
%% https://tex.stackexchange.com/questions/378160/how-to-customize-bibtex-numbering-in-a-document
\makeatletter
\xpatchcmd{\@bibitem}
%  {\item}
  {\H@item}
  {\item[\@biblabel{\changekey{#1}}]}
  {}{}
\xpatchcmd{\@bibitem}
  {\the\value{\@listctr}}
  {\changekey{#1}}
  {}{}
\makeatother

\ExplSyntaxOn
\cs_new:Npn \changekey #1
 {
  \str_case:nVF {#1} \g_changekey_list_tl { ?? }
 }
\cs_new_protected:Npn \setchangekey #1 #2
 {
  \tl_gput_right:Nn \g_changekey_list_tl { {#1}{#2} }
 }
\tl_new:N \g_changekey_list_tl
\cs_generate_variant:Nn \str_case:nnF { nV }
\ExplSyntaxOff

\setchangekey{currat}{10}
\setchangekey{smoothat}{29}
%%END

@@

\maketitle
\thispagestyle{empty}
\appendix

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section*{To Reviewer \#1}

\noindent\textbf{Q1.}
%
\ul{
The DML models are not special in terms of robustness against
adversarial attacks compared to other deep models.
}

\textbf{A:} 
%
We agree with the reviewer. Adversarial robustness at the visual representation
level remains to be an open but insightful problem. Since DML can be
interpreted as ``representation learning in metric space'', we believe the
defense for DML is one step closer to the representation-level robustness,
which is disentangled from specific vision tasks.

\noindent\textbf{Q2.}
%
\ul{
The relationship between the proposed method and a series of
adversarial training algorithms.
}

\cite{smoothat}

### 2022-01-26 reb/RebuttalTemplate.tex

[2]. Zhu, Xiaojin. "An optimal control view of adversarial machine learning." arXiv preprint arXiv:1811.04422 (2018).

\section*{To Reviewer \#2}

\noindent\textbf{Q1.}
%
\ul{
Sentences tend to be too long and complex; Method abbreviations are confusing
and hard to remember.
}

\textbf{A:} Thanks for the suggestion. We will polish the sentences to make
them shorter and simpler, as well as use better abbreviations in the next
revision.

\noindent\textbf{Q2.}
%
\ul{
Tables are hard to grasp at a first glance due to too many abbreviations and
notations.
}

\textbf{A:} Thanks for the suggestion. In order to make the table easier to
read in the next revision, we will (1) extend the captions to make them
self-explanatory; (2) repeat the definitions of symbols and abbreviations in
caption; (3) highlight the columns for imporant performance metrics; (4)
colorize the text abbreviations for different methods in the same way as the
corresponding colored legends in the figures.

### 2022-01-26 reb/RebuttalTemplate.tex

\noindent\textbf{Q1.}
%
\ul{
Sentences tend to be too long and complex; Method abbreviations are confusing
and hard to remember.
}

\textbf{A:} Thanks for the suggestion. We will polish the sentences to make
them shorter and simpler, as well as use better abbreviations in the next
revision.

\noindent\textbf{Q2.}
%
\ul{
Tables are hard to grasp at a first glance due to too many abbreviations and
notations.
}

\textbf{A:} Thanks for the suggestion. In order to make the tables easier to
read in the next revision, we will (1) extend the captions to make them
self-explanatory; (2) repeat the definitions of symbols and abbreviations in
caption; (3) highlight the columns for imporant performance metrics
(\emph{i.e.}, R@1 and ERS); (4) colorize the text abbreviations for different
methods in the same way as the corresponding colored legends in the figures.

\noindent\textbf{Q3.}
%
\ul{
Paragraph on memory and time complexity between methods missing. Are they all
equal?
}

### 2022-01-27 reb/RebuttalTemplate.tex

\textbf{A:} Thanks for the suggestion. We will polish the sentences to make
them shorter and simpler, as well as use better abbreviations in the next
revision.

\noindent\textbf{Q2.}
%
\ul{
Tables are hard to grasp at a first glance due to too many abbreviations and
notations.
}

\textbf{A:} Thanks for the suggestion. In order to make the tables easier to
read in the next revision, we will (1) extend the captions to make them
self-explanatory; (2) repeat the definitions of symbols and abbreviations in
caption; (3) highlight the columns for imporant performance metrics
(\emph{i.e.}, R@1 and ERS); (4) colorize the text abbreviations for different
methods in the same way as the corresponding colored legends in the figures.

\noindent\textbf{Q3.}
%
\ul{
Comparison in memory and time complexity between defense methods is missing. Are they all
equal?
}

\textbf{A:}
%
Not equal but similar in practice.
%
As a common part across methods, PGD has the same
space and time complexities for every sample triplet across methods.
%
The difference in complexities stem from triplet sampling strategy and
adversarial perturbation object functions.
%
In terms of time complexity, EST O(), ACT O(), HM O().
In terms of space complexity, EST O(), ACT O(), HM O().
%
In practice, such difference lead to minor difference in training time
and memory consumption.
%
Take the CUB datset with
$\eta=32$ as example, the TODO.
%
We note these values are sensitive to hardware, software, and
programming tricks, which makes it uneasy for future works to compare.
%
This information in the revised manuscript.

### 2022-01-27 reb/RebuttalTemplate.tex

\maketitle
\thispagestyle{empty}
\appendix

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section*{To Reviewer \#1}

\noindent\textbf{Q1.}
%
\ul{
The DML models are not special in terms of robustness against
adversarial attacks compared to other deep models.
}

\noindent\textbf{A:} 
%
We agree with the reviewer. Robustness at the visual representation
level remains an open problem. Since DML can be
interpreted as ``representation learning in metric space'', we believe the
defense for DML is one step closer to the representation-level robustness,
which is disentangled from specific vision tasks.

\noindent\textbf{Q2.}
%
\ul{
The relationship between the proposed method and a series of
adversarial training algorithms
}(\cite{smoothat,currat,optcontrolaml}).

### 2022-01-28 reb/RebuttalTemplate.tex

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section*{To Reviewer \#1}

\noindent\textbf{Q1.}
%
\ul{
The DML models are not special in terms of robustness against
adversarial attacks compared to other deep models.
}

\noindent\textbf{A:} 
%
We agree with the reviewer. Robustness at the visual representation
level remains an open problem. Since DML can be
interpreted as ``representation learning in metric space'', we believe the
defense for DML is one step closer to the representation-level robustness,
which is disentangled from specific vision tasks.

\noindent\textbf{Q2.}
%
\ul{
The relationship between the proposed method and a series of
adversarial training algorithms}~\cite{smoothat,currat,optcontrolaml}.

@@

\noindent\textbf{Q3.}
%
\ul{
Comparison in memory and time complexity between defense methods is missing. Are they all
equal?
}

\noindent\textbf{A:}
%
Not equal but similar in practice.
%
As a common part across methods, PGD has the same
space and time complexities for every sample triplet across methods.
%
The difference in complexities stem from triplet sampling strategy and
adversarial perturbation object functions.
%
In terms of time complexity, EST O(), ACT O(), HM O().
In terms of space complexity, EST O(), ACT O(), HM O().
%
In practice, such difference lead to minor difference in training time
and memory consumption.
%
Take the CUB datset with
$\eta=32$ as example, the TODO.
%
We note these values are sensitive to hardware, software, and
programming tricks, which makes it uneasy for future works to compare.
%
This information in the revised manuscript.

\section*{To Reviewer \#3}

\noindent\textbf{Q1.}
%
\ul{
Many novel methods have been proposed, e.g., TRADES and AWP.
I wonder whether these methods are not suitable for the metric learning task, and why the robustness of the metric learning task is unique.
}

\noindent\textbf{A:}

\begin{comment}
\noindent\textbf{Q2.} \ul{Does simple tricks for adjusting the hardness.}
\end{comment}

\noindent\textbf{Q2.}
%
Tables (e.g., Tab.3) is hard to read. The authors may need to re-organize them and highlight somewhere.

\noindent\textbf{Q3.}
%
The performance on benign examples seems to drop a lot. Does it mean the HM is just another trade-off way?

\emph{The main motivation of this work is that previous works suffer from excessively hard examples and this work aims to control the hardness.}

### 2022-01-28 reb/RebuttalTemplate.tex

\noindent\textbf{Q1.}
%
\ul{
The DML models are not special in terms of robustness against
adversarial attacks compared to other deep models.
}

\noindent\textbf{A:} 
%
We agree with the reviewer. Robustness at the visual representation
level remains an open problem. Since DML can be
interpreted as ``representation learning in metric space'', we believe the
defense for DML is one step closer to the representation-level robustness,
which is disentangled from specific vision tasks.

\noindent\textbf{Q2.}
%
\ul{
The relationship between the proposed method and a series of
adversarial training algorithms}~\cite{smoothat,currat,optcontrolaml}.

\noindent\textbf{A:}
%
CAT~\cite{currat} creates adversarial examples with gradually increasing
strength (\emph{i.e.}, PGD step) for adversarial training, while our
LGA gradually increases destination hardness $H_\mathsf{D}$ (with a
fixed PGD step) based on loss value.
%
SAT~\cite{smoothat} TODO.
%
Zhu~\emph{et al.}~\cite{optcontrolaml} TODO.
%
We will discuss these similar works in the revised manuscript.

@@

\noindent\textbf{Q1.}
%
\ul{
Many novel methods have been proposed, e.g., TRADES and AWP.
I wonder whether these methods are not suitable for the metric learning task, and why the robustness of the metric learning task is unique.
}

\noindent\textbf{A:}

\begin{comment}
\noindent\textbf{Q2.} \ul{Does simple tricks for adjusting the hardness.}
\end{comment}

\noindent\textbf{Q2.}
%
\ul{Tables (e.g., Tab.~3) are hard to read.}

\noindent\textbf{A:} Thanks for the suggestion. We will improve the tables as described in the answer to Q2 of Reviewer \#2.

### 2022-01-29 reb/RebuttalTemplate.tex

\noindent\textbf{Q1.}
%
\ul{
The DML models are not special in terms of robustness against
adversarial attacks compared to other deep models.
}

\noindent\textbf{A:} 
%
We agree with the reviewer. Robustness at the visual representation
level remains an open problem. Since DML can be
interpreted as ``representation learning in metric space'', we believe the
defense for DML is one step closer to the representation-level robustness,
which is disentangled from specific vision tasks.

\noindent\textbf{Q2.}
%
\ul{
The relationship between the proposed method and a series of
adversarial training algorithms}~\cite{smoothat,currat,optcontrolaml}.

\noindent\textbf{A:}
%
CAT~\cite{currat} uses adversarial examples with gradually increasing strength
(\emph{i.e.}, PGD step), while our LGA gradually increases destination hardness
$H_\mathsf{D}$ (with a fixed PGD step).
%
SAT~\cite{smoothat} gradually increases the difficulty of adversarial examples
in order to achieve smoothness of loss landscape, while our HM is similar to
``early termination of PGD''~\cite{smoothat} with a dynamic ``termination''
threshold determined by LGA.
%
Zhu~\emph{et al.}~\cite{optcontrolaml} TODO.
%
Although these works focus on classification instead of DML, these similarities
will be included in the next reivision.

### 2022-01-29 reb/RebuttalTemplate.tex

\maketitle
\thispagestyle{empty}
\appendix

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section*{To Reviewer \#1}

\noindent\textbf{Q1.}
%
\ul{
The DML models are not special in terms of robustness against
adversarial attacks compared to other deep models.
}

\noindent\textbf{A:} 
%
We agree with the reviewer. Robustness at the visual representation level
remains an open problem. Since DML can be interpreted as ``representation
learning in metric space'' and inspire visual representation learning, we
believe the defense for DML is one step closer to the representation-level
robustness disentangled from specific tasks.

### 2022-01-29 reb/RebuttalTemplate.tex

\noindent\textbf{Q1.}
%
\ul{
The DML models are not special in terms of robustness against
adversarial attacks compared to other deep models.
}

\noindent\textbf{A:} 
%
We agree with the reviewer. Robustness at the visual representation level
remains an open problem. Since DML can be interpreted as ``representation
learning in metric space'' and inspire visual representation learning, we
believe the defense for DML is one step closer to the representation-level
robustness disentangled from specific tasks.

\noindent\textbf{Q2.}
%
\ul{
The relationship between the proposed method and a series of
adversarial training algorithms}~\cite{smoothat,currat,optcontrolaml}.

\noindent\textbf{A:}
%
CAT~\cite{currat} uses adversarial examples with gradually increasing strength
(\emph{i.e.}, PGD step), while our LGA gradually increases destination hardness
$H_\mathsf{D}$ (with a fixed PGD step).
%
SAT~\cite{smoothat} gradually increases the difficulty of adversarial examples
in order to achieve smoothness of loss landscape, while our HM is similar to
``early termination of PGD''~\cite{smoothat} with a dynamic ``termination''
threshold determined by LGA.
%
Zhu~\emph{et al.}~\cite{optcontrolaml} presents an optimal control view of
adversarial machine learning,
%
Although these works focus on classification instead of DML, these similarities
will be included in the next reivision.

@@

\noindent\textbf{Q1.}
%
\ul{
Sentences tend to be too long and complex; Method abbreviations are confusing
and hard to remember.
}

\noindent\textbf{A:} Thanks for the suggestion. We will polish the sentences to make
them shorter and simpler, as well as use better abbreviations in the next
revision.

\noindent\textbf{Q2.}
%
\ul{
Tables are hard to grasp at a first glance due to too many abbreviations and
notations.
}

\noindent\textbf{A:} Thanks for the suggestion.
In the next revision, we will (1) extend the captions to make them
self-explanatory; (2) repeat the definitions of symbols and abbreviations in
caption; (3) highlight the columns for imporant performance metrics
(\emph{i.e.}, R@1 and ERS); (4) colorize the abbreviations for different
defense methods in the same color as their corresponding legends in the figures.

### 2022-01-29 reb/RebuttalTemplate.tex

\noindent\textbf{Q1.}
%
\ul{
The DML models are not special in terms of robustness against
adversarial attacks compared to other deep models.
}

\noindent\textbf{A:} 
%
We agree with the reviewer. Robustness at the visual representation level
remains an open problem. Since DML can be interpreted as ``representation
learning in metric space'' and inspire visual representation learning, we
believe the defense for DML is one step closer to the representation-level
robustness disentangled from specific tasks.

\noindent\textbf{Q2.}
%
\ul{
The relationship between the proposed method and a series of
adversarial training algorithms}~\cite{smoothat,currat,optcontrolaml}.

\noindent\textbf{A:}
%
CAT~\cite{currat} uses adversarial examples with gradually increasing strength
(\emph{i.e.}, PGD step), while our LGA gradually increases destination hardness
$H_\mathsf{D}$ (with a fixed PGD step).
%
SAT~\cite{smoothat} gradually increases the difficulty of adversarial examples
in order to achieve smoothness of loss landscape, while our HM is similar to
``early termination of PGD''~\cite{smoothat} with a dynamic ``termination''
threshold determined by LGA.
%
Zhu~\emph{et al.}~\cite{optcontrolaml} presents an optimal control view of
adversarial machine learning, where our method can also be interpreted as
``adversarial training against test-time attack''.
%
Although these works do not mention DML, these similarities will be included in
the next reivision.

### 2022-01-29 reb/RebuttalTemplate.tex

\noindent\textbf{Q1.}
%
\ul{
The DML models are not special in terms of robustness against
adversarial attacks compared to other deep models.
}

\noindent\textbf{A:} 
%
We agree with the reviewer. Robustness at the visual representation level
remains an open problem. Since DML can be interpreted as ``representation
learning in metric space'' and inspire visual representation learning, we
believe the defense for DML is one step closer to the representation-level
robustness disentangled from specific tasks.

\noindent\textbf{Q2.}
%
\ul{
The relationship between the proposed method and a series of
adversarial training algorithms}~\cite{smoothat,currat,optcontrolaml}.

\noindent\textbf{A:}
%
CAT~\cite{currat} uses adversarial examples with gradually increasing strength
(\emph{i.e.}, PGD step), while our LGA gradually increases destination hardness
$H_\mathsf{D}$ (with a fixed PGD step).
%
SAT~\cite{smoothat} gradually increases the difficulty of adversarial examples
in order to achieve smoothness of loss landscape, while our HM is similar to
``early termination of PGD''~\cite{smoothat} with a dynamic ``termination''
threshold determined by LGA.
%
Zhu~\emph{et al.}~\cite{optcontrolaml} presents an optimal control view of
adversarial machine learning, where our method can also be interpreted as
``adversarial training against test-time attack''.
%
Although they do not mention DML, the similarities will be included in
introduction and related works for next reivision.

@@

\noindent\textbf{Q1.}
%
\ul{
Sentences tend to be too long and complex; Method abbreviations are confusing
and hard to remember.
}

\noindent\textbf{A:} Thanks for the suggestion. We will polish the sentences to make
them shorter and simpler, as well as use better abbreviations in the next
revision.

\noindent\textbf{Q2.}
%
\ul{
Tables are hard to grasp at a first glance due to too many abbreviations and
notations.
}

\noindent\textbf{A:} Thanks for the suggestion.
In the next revision, we will (1) extend the captions to make them
self-explanatory; (2) repeat the definitions of symbols and abbreviations in
captions; (3) highlight the columns for imporant performance metrics
(\emph{i.e.}, R@1 and ERS); (4) colorize the abbreviations for different
defense methods in the same color as their corresponding legends in the
performance curve figures.

### 2022-01-29 reb/RebuttalTemplate.tex

\noindent\textbf{Q1.}
%
\ul{
The DML models are not special in terms of robustness against
adversarial attacks compared to other deep models.
}

\noindent\textbf{A:} 
%
We agree with the reviewer. Robustness at the visual representation level
remains an open problem. Since DML can be interpreted as ``representation
learning in metric space'' and inspire visual representation learning, we
believe the defense for DML is one step closer to the representation-level
robustness disentangled from specific tasks.

\noindent\textbf{Q2.}
%
\ul{
The relationship between the proposed method and a series of
adversarial training algorithms}~\cite{smoothat,currat,optcontrolaml}.

\noindent\textbf{A:}
%
CAT~\cite{currat} uses adversarial examples with gradually increasing strength
(\emph{i.e.}, PGD step), while our LGA gradually increases destination hardness
$H_\mathsf{D}$ (with a fixed PGD step).
%
SAT~\cite{smoothat} gradually increases the difficulty of adversarial examples
in order to achieve smoothness of loss landscape, while our HM is similar to
``early termination of PGD''~\cite{smoothat} with a dynamic ``termination''
threshold determined by LGA.
%
Zhu~\emph{et al.}~\cite{optcontrolaml} presents an optimal control view of
adversarial machine learning, where our method can also be interpreted as
``adversarial training against test-time attack''.
%
Although they do not mention DML, the similarities will be included in
introduction and related works for next revision.

@@

\noindent\textbf{Q1.}
%
\ul{
Sentences tend to be too long and complex; Method abbreviations are confusing
and hard to remember.
}

\noindent\textbf{A:} Thanks for the suggestion. We will polish the sentences to make
them shorter and simpler, as well as use better abbreviations in the next
revision.

\noindent\textbf{Q2.}
%
\ul{
Tables are hard to grasp at a first glance due to too many abbreviations and
notations.
}

\noindent\textbf{A:} Thanks for the suggestion.
In the next revision, we will (1) extend the captions to make them
self-explanatory; (2) repeat the definitions of symbols and abbreviations in
captions; (3) highlight the columns for important performance metrics
(\emph{i.e.}, R@1 and ERS); (4) colorize the abbreviations for different
defense methods in the same color as their corresponding legends in the
performance curve figures.

@@

\noindent\textbf{Q3.}
%
\ul{
Comparison in memory and time complexity between defense methods is missing. Are they all
equal?
}

\noindent\textbf{A:}
%
Not equal but only introduce minor difference in practice.
%
We conduct experiments with two ``Nvidia TITAN Xp'' GPUs on the CUB dataset
with $\eta{=}8$, as follows:
%
\noindent%
\resizebox{1.0\columnwidth}{!}{
\begin{tabular}{c|c|c|c|c}
	\toprule
	 & EST[$\mathcal{S}$]
	 & ACT[$\mathcal{S}$]
	 & HM[$\mathcal{S},g_\mathsf{LGA}$]
	 & HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS \\
	 \midrule
	Time Complexity
	& $\mathcal{O}_\mathsf{PGD} + \mathcal{O}_\mathsf{sampler}$
	& $\mathcal{O}_\mathsf{PGD} + \mathcal{O}_\mathsf{sampler}$
	&
	& \\
	Actual Training Time
	& 2.2hour 
	&
	&
	& \\
	\hline
	Space Complexity & & & & \\
	GPU Memory Usage & & & & \\
	\bottomrule
\end{tabular}
	}
%
The PGD complexities per adversarial
example are identical across different defenses, and hence omitted.
%
As triplet sampler complexities differ across strategies, all defenses use
``Softhard'' for fair comparison in the above table.
%
Apart from these, the complexities stem from the adversarial perturbation
objective functions.
%
Note, the reported values are subject to change in GPU, software, and
programming tricks, \emph{etc.}, which makes them uneasy to compare for future
works.
%
These will be provided in the next revision.

### 2022-01-29 reb/RebuttalTemplate.tex

\noindent\textbf{Q2.}
%
\ul{
Tables are hard to grasp at a first glance due to too many abbreviations and
notations.
}

\noindent\textbf{A:} Thanks for the suggestion.
In the next revision, we will (1) extend the captions to make them
self-explanatory; (2) repeat the definitions of symbols and abbreviations in
captions; (3) highlight the columns for important performance metrics
(\emph{i.e.}, R@1 and ERS); (4) colorize the abbreviations for different
defense methods in the same color as their corresponding legends in the
performance curve figures.

\noindent\textbf{Q3.}
%
\ul{
Comparison in memory and time complexity between defense methods is missing. Are they all
equal?
}

\noindent\textbf{A:}
%
Not equal but only introduce minor difference in practice.
%
We conduct experiments with two ``Nvidia TITAN Xp'' GPUs on the CUB dataset
with $\eta{=}8$, as follows:
%
\noindent%
\resizebox{1.0\columnwidth}{!}{
\begin{tabular}{c|c|c|c|c}
	\toprule
	 & EST[$\mathcal{S}$]
	 & ACT[$\mathcal{S}$]
	 & HM[$\mathcal{S},g_\mathsf{LGA}$]
	 & HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS \\
	 \midrule
	Time Complexity
	& $\mathcal{O}_\mathsf{PGD} + \mathcal{O}_\mathsf{sampler}$
	& $\mathcal{O}_\mathsf{PGD} + \mathcal{O}_\mathsf{sampler}$
	&
	& \\
	Actual Training Time
	& 2.2hour 
	&
	&
	& \\
	\hline
	Space Complexity 
	&
	&
	&
	& \\
	GPU Memory Usage 
	& 
	& 
	& 
	& 8385 MB\\
	\bottomrule
\end{tabular}
	}
%
The PGD complexities per adversarial
example are identical across different defenses, and hence omitted.
%
As triplet sampler complexities differ across strategies, all defenses use
``Softhard'' for fair comparison in the above table.
%
Apart from these, the complexities stem from the adversarial perturbation
objective functions.
%
Note, the reported values are subject to change in GPU, software, and
programming tricks, \emph{etc.}, which makes them uneasy to compare for future
works.
%
These will be provided in the next revision.

@@

\section*{To Reviewer \#3}

\noindent\textbf{Q1.}
%
\ul{Many methods have been proposed, e.g., TRADES}\cite{trades} \ul{and AWP.
I wonder whether these methods are not suitable for the metric learning task, and why the robustness of the metric learning task is unique.
}

@@

\begin{comment}
\noindent\textbf{Q2.} \ul{Does simple tricks for adjusting the hardness.}
\end{comment}

\noindent\textbf{Q2.}
%
\ul{Tables (e.g., Tab.~3) are hard to read.}

\noindent\textbf{A:} Thanks for the suggestion. We will improve the tables as described in the answer to Q2 of Reviewer \#2.

\noindent\textbf{Q3.}
%
\ul{The performance on benign examples seems to drop a lot. Does it mean the
HM is just another trade-off way?}

### 2022-03-02 robdml.tex
tex
remove unnecessary acks.
robdml

@@

\textbf{Adversarial Defense.}
%
Various defenses are proposed to counter the attacks.
%
However, defenses incurring gradient masking
lead to a false sense of robustness~\cite{obfuscated}.
%
Defensive distillation~\cite{distill2} is compromised in~\cite{cw}.
%
Ensemble of weak defenses is not
robust~\cite{ensembleweak}.
%
Other defenses such as input
preprocessing~\cite{deflecting}, or randomization~\cite{self-ensemble} are proposed.
%
But many of them are still susceptible to adaptive attacks~\cite{adaptive}.
%
Of all defenses, adversarial training~\cite{madry} consistently remains to be one of the
most effective
methods~\cite{bilateral,advtrain-triplet,benchmarking,smoothat,trades,robustwrn,weightperturb,featurescatter},
but suffers from high training cost~\cite{freeat,fastat,yopo}, performance drop on
benign examples~\cite{odds,geometry,onmanifold}, and overfitting on adversarial examples~\cite{bagoftricks,overfitting}.

@@

>>>>

\definecolor{cyan}{rgb}{0.0, 0.72, 0.92}

@@

\textbf{Adversarial Defense.}
%
Various defenses are proposed to counter the attacks.
%
However, defenses incurring gradient masking
lead to a false sense of robustness~\cite{obfuscated}.
%
Defensive distillation~\cite{distill2} is compromised in~\cite{cw}.
%
Ensemble of weak defenses is not
robust~\cite{ensembleweak}.
%
Other defenses such as input
preprocessing~\cite{deflecting}, or randomization~\cite{self-ensemble} are proposed.
%
But many of them are still susceptible to adaptive attacks~\cite{adaptive}.
%
Of all defenses, adversarial training~\cite{madry} consistently remains to be one of the
most effective
methods~\cite{bilateral,advtrain-triplet,benchmarking,smoothat,trades,robustwrn,weightperturb,featurescatter,currat,awp},
but suffers from high training cost~\cite{freeat,fastat,yopo}, performance drop on
benign examples~\cite{odds,geometry,onmanifold}, and overfitting on adversarial examples~\cite{bagoftricks,overfitting}.

@@

\textbf{Acknowledgements.} This research was supported by []. We thank
Kangfu Mei for helpful discussions and feedbacks.
